On pulsed microwave acoustic resonant viral inactivation: summary

### 2020-07-25 documents/pamphlet.tex
Driver built

If this is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized.

@@

@@

With modern semiconductor processes, it is trivial to produce

It is possible to create these conditions within human tissues; attenuation limits the safe treatment depth to about 3 cm.

>>>>

If this is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns.

@@

It is possible to create these conditions within human tissues. Depending on the type of tissue, this field strength appears to be safely produced a minimum of 3 cm thickness (suitable for targeted sterilization of lungs etc with a bronchoscopic technique), up to 200 cm (entirely removing the virus from the body). \ghfile{documents/pulse.ipynb} We await the reply

On an individual level, the free-space-combined output of, say, a few dozen SiGe:C or GaAs transistors (\$0.3 apiece [BFP620]) should suffice to locally protect the major vulnerabilities like mouth, nose, eyes, hair and any surfaces that the hands contact. This arguably wouldn't provide many advantages over simple masks, however.
\ghfile{documents/global.ipynb}

@@
